Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2025-12-02 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
ClassicalLimit: added paragraph for the figure

>>>>

In Fig.~\ref{fig:cat_streatched} we show a cat state as it is being stretched. Note that the stretching necessarily lowers the norm of the pseudo-probability density of both positive and negative regions. However, as expected, the negative regions are dampened much faster. After a stretching factor of $\lambda = 5$, the negative parts are negligible compared to the positive parts.
